Hierarchical storage management in user space for neuroimaging applications

### 2025-10-16 paper/sea-neuro/paper-neuro.tex
Add few more paper edits

    Sea (\autoref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls, or more specifically, file access calls to the GNU C library,
    glibc, on Linux systems. Its goal is to easily enable users to intergrate efficient data management within their
    applications within their existing workflows. Using glibc interception, Sea can redirect write calls
    aimed at slower storage devices to a faster device whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini} (\autoref{lst:seaini}). This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

@@

    \vhs{Sea can run alongside any application that dynamically loads and calls the libc library for read/write operations. Such applications commonly include interpreted applications, such as Python and Matlab/Octave. Sea can additionally work seamlessly from within a containerized environment, as long as the necessary cache directories required by Sea are mounted to the container. We provide various Docker containers preinstalled with Sea within the Github Container Registry (\url{https://github.com/orgs/big-data-lab-team/packages?repo_name=Sea}). Alternatively, Sea can be compiled from source using Make.} Once
    compiled, Sea can be executed using the \texttt{sea\_launch.sh} bash script.

@@

    Each tool was set to only run the functional preprocessing pipeline. For the FSL preprocessing pipeline, 
    we used FEAT configured with many of
    the default parameters. We set the following parameters: slice-timing
    correction (interleaved), intensity normalization and non-linear
    registration to standard space. FSL version 6.0.4 was used.

    %% Add SPM here
    To preprocess the datasets with SPM, we reused the template described in
    \cite{haitas2021age}, with fieldmap correction removed. \vhs{As with the other applications, MNI registration was performed.} Since the template was
    designed for a specific dataset, we updated the paths to the fMRI and
    anatomical images, as well as the dimensions, such as the number of volumes
    and slices and the TR and TA, for each dataset. Furthermore, we set the
    slice order to interleaved in all cases. SPM version 12 was used.

    For AFNI preprocessing, the pipeline was configured to perform slice timing, \vhs{EPI alignment to anatomical, 
    linear alignment to MNI space,} registration, smoothing \vhs{(blur size of 4)} and brain masking.
    While AFNI does have some parallelized components that can be controlled via
    environment variables, we chose to let the pipeline use as much parallelism
    as required for its execution. AFNI version 21.1.02 was used.

@@

Baseline performance without busy writers was comparable to that of Sea's (p=0.7, two-sample unpaired t-test) as can be seen in Figure~\ref{fig:seaneuro:slashbin}. However, with
busy writers, the makespan obtained with Sea was smaller than baseline (p<1e-04, two-sample t-test). Occassional slowdowns did occur with the use of Sea. These slowdowns
may arise from the initial read of the data, as they appeared to occur less
frequently with the SPM pipeline, or due to increased CPU contention caused by Sea's rapid I/O.

@@

    Scripts used to
    execute each pipeline can be found
    at~\url{https://github.com/valhayot/sea-slurm-scripts}. 
    Dockerfiles containing AFNI, SPM, and FSL with Sea pre-installed are available
    at~\url{https://github.com/ValHayot/Sea/tree/master/containers/applications}.

>>>>

    Sea (\autoref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls, or more specifically, file access calls to the GNU C library,
    glibc, on Linux systems. Its goal is to easily enable users to intergrate efficient data management within their
    applications within their existing workflows. \vhs{Sea benefits most applications that process large quantities of data. These can include applications that process large files, as they would benefit from increased bandwidth provided by faster storage devices, as well as large quantities of small files, as such applications would benefit from decreased latency brought on by higher performance storage devices. Applications relying on shared filesystems whose performance may be affected by other user behaviour may also benefit from Sea usage, as node-local temporary storage is most commonly dedicated to the user's in HPC environments}.

    With glibc interception, Sea can redirect write calls
    aimed at slower storage devices to a faster device whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini} (\autoref{lst:seaini}). This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

@@

    \vhs{Sea can run alongside any application that dynamically loads and calls the libc library for read/write operations. Such applications commonly include interpreted applications, such as Python and Matlab/Octave. Sea can additionally work seamlessly from within a containerized environment, as long as the necessary cache directories required by Sea are mounted to the container. We provide various Docker containers preinstalled with Sea within the Github Container Registry\footnote{\url{https://github.com/orgs/big-data-lab-team/packages?repo_name=Sea}}. Alternatively, Sea can be compiled from source using Make.} Once
    compiled, Sea can be executed using the \texttt{sea\_launch.sh} bash script.

@@

    Each tool was set to only run the functional preprocessing pipeline. For the FSL preprocessing pipeline, 
    we used FEAT configured with many of
    the default parameters. We set the following parameters: slice-timing
    correction (interleaved), intensity normalization and non-linear
    registration to standard space. \vhs{Outputted files were compressed NIfTI (.nii.gz) format.} FSL version 6.0.4 was used.

    %% Add SPM here
    To preprocess the datasets with SPM, we reused the template described in
    \cite{haitas2021age}, with fieldmap correction removed. \vhs{SPM was configured to perform slice timing correction, motion correction for within-subject registration, structural alignment to standard space MNI template, and an 8mm gaussian blur.} Since the template was
    designed for a specific dataset, we updated the paths to the fMRI and
    anatomical images, as well as the dimensions, such as the number of volumes
    and slices and the TR and TA, for each dataset. Furthermore, we set the
    slice order to interleaved in all cases. \vhs{Output files were in uncompressed NIfTI (.nii) format.} SPM version 12 was used.

    For AFNI preprocessing, the pipeline was configured to perform slice timing correction, \vhs{EPI alignment to anatomical with robust motion correction, 
    warping of both anatomical and EPI to MNI space,} smoothing \vhs{(blur size of 4)} and brain masking.
    While AFNI does have some parallelized components that can be controlled via
    environment variables, we chose to let the pipeline use as much parallelism
    as required for its execution. \vhs{Output files generated were in uncompressed .BRIK/.HEAD format.} AFNI version 21.1.02 was used.

@@

Baseline performance without busy writers was comparable to that of Sea's (p=0.7, two-sample unpaired t-test) as can be seen in Figure~\ref{fig:seaneuro:slashbin}. However, with
busy writers, the makespan obtained with Sea was smaller than baseline (p<1e-04, two-sample t-test). Occasional slowdowns did occur with the use of Sea. These slowdowns
may arise from the initial read of the data, as they appeared to occur less
frequently with the SPM pipeline, or due to increased CPU contention caused by Sea's rapid I/O.

@@

    Scripts used to
    execute each pipeline can be found
    at~\url{https://github.com/valhayot/sea-slurm-scripts}. 
    Dockerfiles containing AFNI, SPM, and FSL with Sea pre-installed are available
    at~\url{https://github.com/big-data-lab-team/Sea/tree/main/containers/applications}. Sea implementation is available at \url{https://github.com/big-data-lab-team/Sea}.
